\section{研究成果}
\subsection{已发表论文}

\begin{frame}
  \frametitle{已发表论文}
  \textbf{Xuan Mao}, Yuxiang Li.
  Critical Mass for Keller-Segel Systems with Supercritical Nonlinear Sensitivity. 
  \emph{Math. Models Methods Appl. Sci.}, 2023, 33(11): 2395--2423.
  %\url{https://doi.org/10.1142/S0218202523400079}
  %\href{https://doi.org/10.1142/S0218202523400079}{doi:10.1142/S0218202523400079}
  \hfill (数学会T1; 中科院1区; JCR: Q1)\\
  \textbf{Xuan Mao}, Yuxiang Li. 
  Dirac-type aggregation with full mass in a chemotaxis model. 
  \emph{Discrete Contin. Dyn. Syst. Ser. S.}, 2024, 17(4):1513--1528. 
  %\url{https://doi.org/10.3934/dcdss.2023185}
  %\href{https://doi.org/10.3934/dcdss.2023185}{doi:10.3934/dcdss.2023185}
  \hfill (数学会T4; 中科院4区; JCR: Q2)\\
  \textbf{Xuan Mao}, Yuxiang Li. 
  Instability of homogeneous steady states in chemotaxis systems with flux limitation, 
  \emph{Nonlinear Anal.}, 2024, 243: Paper No. 113527, 18.
      %\url{https://doi.org/10.1016/j.na.2024.113527}
  \hfill (数学会T3; 中科院2区; JCR: Q1)
  \end{frame}

\subsection{已完成工作}

\begin{frame}
  \frametitle{已完成工作}
  \textbf{Xuan Mao}, Yuxiang Li. 
  A note on the $8\pi$ problem of J\"ager-Luckhaus system.
  \href{https://doi.org/10.48550/arXiv.2405.06315}
  {arXiv: 2405.06315}.\\ 
  \textbf{Xuan Mao}, Yuxiang Li.
  Global solvability and unboundedness in a fully parabolic quasilinear chemotaxis model with indirect signal production.
  %arXiv preprint, 2024, 
  \href{https://arxiv.org/abs/2410.13238}
  {arXiv: 2410.13238}.\\
  \textbf{Xuan Mao}, Yuxiang Li. Finite-time blowup in a five- and higher-dimensional chemotaxis model with indirect signal production. %arXiv preprint 2024, 
\href{https://arxiv.org/pdf/2412.10772}{arXiv: 2412.10772}.\\
\end{frame}

\section{学术活动/服务}

\begin{frame}{学术活动/服务}
  \begin{itemize}
    \item 2023.08.23--25, 2023年生物数学趋化模型学术研讨会, 成都, 西华大学/电子科技大学
    \item 2024.03.24--25, The recent progress in chemotaxis and prey-taxis models, Hong Kong, Department of Applied Mathematics, The Hong Kong Polytechnic University
    \item Journal of Evolution Equations 匿名审稿人 \hfill 2024.11 起
  \end{itemize}
\end{frame}